### 2022-05-13 main/draft.tex
add junk tex file

\chapter{Searches in ATLAS}
\label{chapter:intro}

\epigraph{%
One way is to make it so simple that there are \emph{obviously} no deficiencies and the other way is to make it so complicated that there are
no \emph{obvious} deficiencies.%
}%
{Tony Hoare~\cite{hoare2007emperor}}

\section{Data analysis}

\section{Frequentist theory}

\epigraph{%
Within this theory, statistical methods of great practical usefulness have been
developed, and its statements can and frequently do contribute in a vague way
to the interpretation of data. \ldots%
}%
{John W. Pratt~\cite{pratt1961testing}}

\section{Post-frequentist practice}

\epigraph{%
\ldots\ But this book, by its very excellence, its thoroughness, lucidity and
precision, intensifies my growing feeling that nevertheless the theory is
arbitrary, be it however ``objective,'' and the problems it solves, however
precisely it may solve them, are not even simplified theoretical counterparts
of the real problems to which it is applied.%
}%
{John W. Pratt~\cite{pratt1961testing}}

% significancen measures
The ATLAS-recommended~\cite{atlas_significance} significance measure is
\begin{equation}
\label{eqn:significance_atlas}
S_\mathrm{ATLAS}(n, \mu, \sigma)
= \mathrm{sgn}(n - \mu) \sqrt{2\left(
    n\log\left(\frac{n(\mu + \sigma^2)}{\mu^2 + n\sigma^2}\right)
    - \frac{\mu^2}{\sigma^2}\log\left(
        1 + \frac{\sigma^2(n - \mu)}{\mu(\mu + \sigma^2)}
    \right)
\right)}
~.
\end{equation}
As $\sigma \rightarrow 0$, this tends towards the the significance-transformed,
sign-flipped Poisson maximum likelihood ratio
\begin{equation}
S_\mathrm{Poisson}(n, \mu, \sigma)
= \mathrm{sgn}(n - \mu) \sqrt{2\left(
    n\log\left(\frac{n}{\mu}\right) - n + \mu
\right)}
~.
\end{equation}

\section{Searches}

\clearpage

Hello again

>>>>

As $\sigma \rightarrow 0$, this tends towards the the significance-transformed,
sign-flipped Poisson maximum likelihood ratio
\begin{equation}
S_\mathrm{Poisson}(n, \mu, \sigma)
= \mathrm{sgn}(n - \mu) \sqrt{2\left(
    n\log\left(\frac{n}{\mu}\right) - n + \mu
\right)}
~.
\end{equation}
